COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries: Replication Code

### 2021-06-22 paper_files/figure-latex/mainfigure1-1.tex
update

% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:22
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}

@@

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (650.43,542.02);
\end{scope}
\begin{scope}
\path[clip] (152.00, 76.80) rectangle (271.61,506.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (152.00, 76.80) rectangle (271.61,506.36);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (171.03, 76.80) --
	(171.03,506.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (198.21, 76.80) --
	(198.21,506.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (225.40, 76.80) --
	(225.40,506.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (252.58, 76.80) --
	(252.58,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00, 92.71) --
	(271.61, 92.71);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,119.23) --
	(271.61,119.23);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,145.75) --
	(271.61,145.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,172.26) --
	(271.61,172.26);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,198.78) --
	(271.61,198.78);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,225.29) --
	(271.61,225.29);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,251.81) --
	(271.61,251.81);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,278.33) --
	(271.61,278.33);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,304.84) --
	(271.61,304.84);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,331.36) --
	(271.61,331.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,357.87) --
	(271.61,357.87);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,384.39) --
	(271.61,384.39);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,410.91) --
	(271.61,410.91);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,437.42) --
	(271.61,437.42);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,463.94) --
	(271.61,463.94);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,490.45) --
	(271.61,490.45);

\path[draw=drawColor,line width= 0.5pt,line join=round] (157.44, 76.80) --
	(157.44,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (184.62, 76.80) --
	(184.62,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (211.80, 76.80) --
	(211.80,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (238.99, 76.80) --
	(238.99,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (266.17, 76.80) --
	(266.17,506.36);
\definecolor{drawColor}{RGB}{204,102,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.51,143.09) --
	(250.51,148.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.51,145.75) --
	(238.88,145.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (238.88,143.09) --
	(238.88,148.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (233.01,487.80) --
	(233.01,493.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] (233.01,490.45) --
	(226.48,490.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] (226.48,487.80) --
	(226.48,493.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] (241.81,461.29) --
	(241.81,466.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (241.81,463.94) --
	(235.94,463.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (235.94,461.29) --
	(235.94,466.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.38,434.77) --
	(251.38,440.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.38,437.42) --
	(247.47,437.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.47,434.77) --
	(247.47,440.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (257.15,408.25) --
	(257.15,413.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (257.15,410.91) --
	(251.49,410.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.49,408.25) --
	(251.49,413.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (263.56,381.74) --
	(263.56,387.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (263.56,384.39) --
	(261.28,384.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] (261.28,381.74) --
	(261.28,387.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (242.47,355.22) --
	(242.47,360.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (242.47,357.87) --
	(238.23,357.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] (238.23,355.22) --
	(238.23,360.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (246.92,328.71) --
	(246.92,334.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (246.92,331.36) --
	(233.55,331.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (233.55,328.71) --
	(233.55,334.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (232.35,302.19) --
	(232.35,307.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (232.35,304.84) --
	(227.13,304.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (227.13,302.19) --
	(227.13,307.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (191.91,116.58) --
	(191.91,121.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (191.91,119.23) --
	(189.08,119.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (189.08,116.58) --
	(189.08,121.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.82,275.67) --
	(251.82,280.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.82,278.33) --
	(247.58,278.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.58,275.67) --
	(247.58,280.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.97,249.16) --
	(244.97,254.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.97,251.81) --
	(239.53,251.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (239.53,249.16) --
	(239.53,254.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.86,222.64) --
	(254.86,227.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.86,225.29) --
	(251.17,225.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.17,222.64) --
	(251.17,227.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (252.25,196.13) --
	(252.25,201.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (252.25,198.78) --
	(249.21,198.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (249.21,196.13) --
	(249.21,201.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (243.01,169.61) --
	(243.01,174.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (243.01,172.26) --
	(238.23,172.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (238.23,169.61) --
	(238.23,174.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.61, 90.06) --
	(230.61, 95.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.61, 92.71) --
	(224.63, 92.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (224.63, 90.06) --
	(224.63, 95.37);
\definecolor{fillColor}{RGB}{204,102,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (244.75,145.75) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (229.74,490.45) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (238.88,463.94) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (249.43,437.42) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (254.32,410.91) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (262.47,384.39) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (240.29,357.87) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (240.18,331.36) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (229.74,304.84) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.49,119.23) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (249.75,278.33) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (242.25,251.81) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (253.01,225.29) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (250.73,198.78) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (240.62,172.26) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (227.68, 92.71) circle (  1.96);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.00,159.00) -- (271.61,159.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.00,132.49) -- (271.61,132.49);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] (152.00, 76.80) rectangle (271.61,506.36);
\end{scope}
\begin{scope}
\path[clip] (276.61, 76.80) rectangle (396.21,506.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (276.61, 76.80) rectangle (396.21,506.36);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (295.64, 76.80) --
	(295.64,506.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (322.82, 76.80) --
	(322.82,506.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (350.00, 76.80) --
	(350.00,506.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (377.19, 76.80) --
	(377.19,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61, 92.71) --
	(396.21, 92.71);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,119.23) --
	(396.21,119.23);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,145.75) --
	(396.21,145.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,172.26) --
	(396.21,172.26);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,198.78) --
	(396.21,198.78);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,225.29) --
	(396.21,225.29);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,251.81) --
	(396.21,251.81);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,278.33) --
	(396.21,278.33);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,304.84) --
	(396.21,304.84);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,331.36) --
	(396.21,331.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,357.87) --
	(396.21,357.87);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,384.39) --
	(396.21,384.39);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,410.91) --
	(396.21,410.91);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,437.42) --
	(396.21,437.42);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,463.94) --
	(396.21,463.94);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,490.45) --
	(396.21,490.45);

\path[draw=drawColor,line width= 0.5pt,line join=round] (282.04, 76.80) --
	(282.04,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (309.23, 76.80) --
	(309.23,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (336.41, 76.80) --
	(336.41,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (363.59, 76.80) --
	(363.59,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (390.78, 76.80) --
	(390.78,506.36);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (374.36,148.40) --
	(374.36,151.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (374.36,149.72) --
	(361.75,149.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (361.75,148.40) --
	(361.75,151.05);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (377.73,140.44) --
	(377.73,143.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] (377.73,141.77) --
	(366.20,141.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (366.20,140.44) --
	(366.20,143.09);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (355.87,493.10) --
	(355.87,495.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (355.87,494.43) --
	(343.26,494.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (343.26,493.10) --
	(343.26,495.76);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (360.22,485.15) --
	(360.22,487.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] (360.22,486.48) --
	(352.72,486.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (352.72,485.15) --
	(352.72,487.80);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (365.77,466.59) --
	(365.77,469.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (365.77,467.91) --
	(358.27,467.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (358.27,466.59) --
	(358.27,469.24);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (370.88,458.63) --
	(370.88,461.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (370.88,459.96) --
	(361.42,459.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (361.42,458.63) --
	(361.42,461.29);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (373.49,440.07) --
	(373.49,442.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (373.49,441.40) --
	(366.42,441.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (366.42,440.07) --
	(366.42,442.72);
\definecolor{drawColor}{RGB}{68,170,153}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2021-06-22 11:48:04
% !TEX encoding = UTF-8 Unicode
% !TEX program = xelatex

\documentclass[fontsize=7pt,DIV=calc]{scrartcl}

@@

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (650.43,542.02);
\end{scope}
\begin{scope}
\path[clip] (123.21, 72.04) rectangle (250.02,511.66);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (123.21, 72.04) rectangle (250.02,511.66);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (143.39, 72.04) --
	(143.39,511.66);

\path[draw=drawColor,line width= 0.3pt,line join=round] (172.21, 72.04) --
	(172.21,511.66);

\path[draw=drawColor,line width= 0.3pt,line join=round] (201.03, 72.04) --
	(201.03,511.66);

\path[draw=drawColor,line width= 0.3pt,line join=round] (229.84, 72.04) --
	(229.84,511.66);

\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21, 87.37) --
	(250.02, 87.37);

\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,112.93) --
	(250.02,112.93);

\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,138.49) --
	(250.02,138.49);

\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,164.05) --
	(250.02,164.05);

\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,189.61) --
	(250.02,189.61);

\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,215.17) --
	(250.02,215.17);

\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,240.73) --
	(250.02,240.73);

\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,266.29) --
	(250.02,266.29);

\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,291.85) --
	(250.02,291.85);

\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,317.41) --
	(250.02,317.41);

\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,342.97) --
	(250.02,342.97);

\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,368.53) --
	(250.02,368.53);

\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,394.09) --
	(250.02,394.09);

\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,419.65) --
	(250.02,419.65);

\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,445.21) --
	(250.02,445.21);

\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,470.77) --
	(250.02,470.77);

\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,496.33) --
	(250.02,496.33);

\path[draw=drawColor,line width= 0.5pt,line join=round] (128.98, 72.04) --
	(128.98,511.66);

\path[draw=drawColor,line width= 0.5pt,line join=round] (157.80, 72.04) --
	(157.80,511.66);

\path[draw=drawColor,line width= 0.5pt,line join=round] (186.62, 72.04) --
	(186.62,511.66);

\path[draw=drawColor,line width= 0.5pt,line join=round] (215.44, 72.04) --
	(215.44,511.66);

\path[draw=drawColor,line width= 0.5pt,line join=round] (244.25, 72.04) --
	(244.25,511.66);
\definecolor{drawColor}{RGB}{204,102,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.57,135.93) --
	(231.57,141.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.57,138.49) --
	(207.25,138.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.25,135.93) --
	(207.25,141.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (227.65,161.49) --
	(227.65,166.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (227.65,164.05) --
	(215.32,164.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (215.32,161.49) --
	(215.32,166.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.10,493.77) --
	(209.10,498.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.10,496.33) --
	(202.18,496.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (202.18,493.77) --
	(202.18,498.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (218.43,468.21) --
	(218.43,473.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] (218.43,470.77) --
	(212.21,470.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (212.21,468.21) --
	(212.21,473.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.46,442.65) --
	(228.46,447.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.46,445.21) --
	(223.85,445.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (223.85,442.65) --
	(223.85,447.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (234.69,417.09) --
	(234.69,422.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] (234.69,419.65) --
	(228.69,419.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.69,417.09) --
	(228.69,422.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] (241.49,391.53) --
	(241.49,396.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (241.49,394.09) --
	(239.07,394.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] (239.07,391.53) --
	(239.07,396.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (219.12,365.97) --
	(219.12,371.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (219.12,368.53) --
	(214.63,368.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.63,365.97) --
	(214.63,371.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (223.85,340.41) --
	(223.85,345.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (223.85,342.97) --
	(209.67,342.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.67,340.41) --
	(209.67,345.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (208.40,314.85) --
	(208.40,319.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (208.40,317.41) --
	(202.87,317.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (202.87,314.85) --
	(202.87,319.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.52,110.37) --
	(165.52,115.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.52,112.93) --
	(162.52,112.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.52,110.37) --
	(162.52,115.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.04,289.29) --
	(229.04,294.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.04,291.85) --
	(224.54,291.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (224.54,289.29) --
	(224.54,294.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (221.78,263.73) --
	(221.78,268.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (221.78,266.29) --
	(216.01,266.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.01,263.73) --
	(216.01,268.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (232.27,238.17) --
	(232.27,243.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] (232.27,240.73) --
	(228.35,240.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.35,238.17) --
	(228.35,243.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.50,212.61) --
	(229.50,217.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.50,215.17) --
	(226.27,215.17);

\path[draw=drawColor,line width= 0.6pt,line join=round] (226.27,212.61) --
	(226.27,217.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] (219.70,187.05) --
	(219.70,192.17);

\path[draw=drawColor,line width= 0.6pt,line join=round] (219.70,189.61) --
	(214.63,189.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.63,187.05) --
	(214.63,192.17);

\path[draw=drawColor,line width= 0.6pt,line join=round] (206.56, 84.82) --
	(206.56, 89.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] (206.56, 87.37) --
	(200.22, 87.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] (200.22, 84.82) --
	(200.22, 89.93);
\definecolor{fillColor}{RGB}{204,102,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (219.35,138.49) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (221.55,164.05) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (205.64,496.33) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (215.32,470.77) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (226.16,445.21) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (231.69,419.65) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (240.34,394.09) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (216.82,368.53) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (216.70,342.97) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (205.64,317.41) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.02,112.93) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (226.85,291.85) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (218.89,266.29) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (230.31,240.73) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (227.89,215.17) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (217.16,189.61) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (203.45, 87.37) circle (  1.96);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (123.21,176.83) -- (250.02,176.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (123.21,151.27) -- (250.02,151.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (123.21,125.71) -- (250.02,125.71);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] (123.21, 72.04) rectangle (250.02,511.66);
\end{scope}
\begin{scope}
\path[clip] (255.02, 72.04) rectangle (381.82,511.66);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (255.02, 72.04) rectangle (381.82,511.66);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (275.19, 72.04) --
	(275.19,511.66);

\path[draw=drawColor,line width= 0.3pt,line join=round] (304.01, 72.04) --
	(304.01,511.66);

\path[draw=drawColor,line width= 0.3pt,line join=round] (332.83, 72.04) --
	(332.83,511.66);

\path[draw=drawColor,line width= 0.3pt,line join=round] (361.65, 72.04) --
	(361.65,511.66);

\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02, 87.37) --
	(381.82, 87.37);

\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,112.93) --
	(381.82,112.93);

\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,138.49) --
	(381.82,138.49);

\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,164.05) --
	(381.82,164.05);

\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,189.61) --
	(381.82,189.61);

\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,215.17) --
	(381.82,215.17);

\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,240.73) --
	(381.82,240.73);

\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,266.29) --
	(381.82,266.29);

\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,291.85) --
	(381.82,291.85);

\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,317.41) --
	(381.82,317.41);

\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,342.97) --
	(381.82,342.97);

\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,368.53) --
	(381.82,368.53);

\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,394.09) --
	(381.82,394.09);

\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,419.65) --
	(381.82,419.65);

\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,445.21) --
	(381.82,445.21);

\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,470.77) --
	(381.82,470.77);

\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,496.33) --
	(381.82,496.33);

\path[draw=drawColor,line width= 0.5pt,line join=round] (260.78, 72.04) --
	(260.78,511.66);

\path[draw=drawColor,line width= 0.5pt,line join=round] (289.60, 72.04) --
	(289.60,511.66);

\path[draw=drawColor,line width= 0.5pt,line join=round] (318.42, 72.04) --
	(318.42,511.66);

\path[draw=drawColor,line width= 0.5pt,line join=round] (347.24, 72.04) --
	(347.24,511.66);

\path[draw=drawColor,line width= 0.5pt,line join=round] (376.06, 72.04) --
	(376.06,511.66);
\definecolor{drawColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.6pt,line join=round] (361.65,141.05) --
	(361.65,143.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] (361.65,142.32) --
	(334.10,142.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] (334.10,141.05) --
	(334.10,143.60);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (364.99,133.38) --
	(364.99,135.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] (364.99,134.66) --
	(341.71,134.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (341.71,133.38) --
	(341.71,135.93);
\definecolor{drawColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.6pt,line join=round] (358.77,166.61) --
	(358.77,169.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] (358.77,167.88) --
	(345.39,167.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (345.39,166.61) --
	(345.39,169.16);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (362.11,158.94) --
	(362.11,161.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (362.11,160.22) --
	(350.01,160.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] (350.01,158.94) --
	(350.01,161.49);
\definecolor{drawColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.6pt,line join=round] (339.05,498.88) --
	(339.05,501.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] (339.05,500.16) --
	(325.68,500.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] (325.68,498.88) --
	(325.68,501.44);
\definecolor{drawColor}{RGB}{153,153,51}
